---
title: "Lab 01 - Hello R"
author: "laurenlatham97"
date: "2/2/21"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

This data set has 1846 rows and 3 columns. The variables are 1) the data set, 2) the x values, and 3) the y values. 

### Exercise 2

Below is the dino data plotted with its correlation coefficient. 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation between x and y is -.0645

### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The star data set forms a star shape. So a correlation doesn't make much more sense, but as you can see below the correlation is -.0630.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Below is the plotted circle data and correlation. Again, a correlation doesn't make much sense given the shape of the data, but it's -.0683. 

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Below are plots of all of the data sets with correlation coefficients. 

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

