---
title: "Lab 01 - Hello R"
author: "laurenlatham97"
date: "2/2/21"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

This data set has 1846 rows and 3 columns. The variables are 1) the data set, 2) the x values, and 3) the y values. 

### Exercise 2

The answers for this Exercise are given for you below.
But you should clean up some of the narrative so that it only includes what you want to turn in.


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation between x and y is -.0645

### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The star data set forms a star shape. So a correlation doesn't make much more sense, but as you can see below the correlation is -.0630.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.
To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.
